{\small
\begin{thebibliography}{99}

\bibitem{mentor} 0-In Formal Verification. 
	http://www.mentor.com/products/fv/abv/0-in\_fv/index.cfm

\bibitem{aagard} Aagard, M., Jones, R., and Segar, C.-J., Combining
        theorem proving and trajectory evaluation in an industrial
        environment, In {\em Proc. of Design Automation Conference (DAC)}, 
	1998, pp. 538-541.

\bibitem{abadi:95} Abadi, M. and Lamport, L., Conjoining Specifications,
	In {\em ACM Transactions of Programming Languages and Systems
	(TOPLAS)}, Volume 17, Issue 3, pp. 507-535, 1995.

\bibitem {abraham:02}  Abraham, J.A., Vedula, V.M., and Saab, D.G., Verifying
	Properties Using Sequential ATPG. In {\em Proc. of International
        Test Conference (ITC)}, pp. 194-202, 2002.

\bibitem{Abr80} Abrial, J.R., The Specification Language Z: Syntax and 
		Semantics", Program Research Group, Oxford University, 1980.

\bibitem{Abr96} Abrial, J.R., The B-Book: Assigning Programs to Meanings, 
		Cambridge University Press, 1996

\bibitem{gurevich} {\em Abstract State Machines: Verification},
        http://www.eecs.umich.edu/gasm 

\bibitem{accellera} ACCELLERA homepage, http://www.accellera.org

\bibitem{alur:04} Alur, R., and Torre, S. La, Deterministic
    generators and games for LTL fragments, ACM
    Trans. Comput. Logic, 5(1) pp. 1-25, 2004

\bibitem{alur:94} Alur, R., and Henzinger, T.A., A really temporal logic.
	{\em Journal of the ACM}, 41 (1), pp. 181-204, 1994.

\bibitem{amla1} Amla, N., Emerson, E.A., Namjoshi, K.S. and Trefler, R.,
        Assume-guarantee based compositional reasoning for synchronous
        timing diagrams. In Proceedings of
        {\em International Conference on Tools and Algorithms for the
        Construction and Analysis of Systems (TACAS)}, volume 2031 of LNCS,
        pp. 465-479, 2001.

\bibitem{amla2} Amla, N., Emerson, E.A., Kurshan, R.P. and Namjoshi, K.S.,
        RTDT: A Front-End for Efficient Model Checking of Synchronous
        Timing Diagrams,
        In Proceedings of {\em International Conference on Computer Aided
        Verification (CAV)}, pp. 387-390, 2001. 

\bibitem{amla3} Amla, N., Emerson, E.A. and Namjoshi, K.S.,
        Efficient Decompositional Model checking for Regular Timing
        diagrams, In Proceedings of {\em International Conference on Correct
        Hardware Design and Verification Methods (CHARME)}, pp. 67-81, 1999.

\bibitem{amla5} Amla, N., Emerson, E.A., Namjoshi, K.S. and Trefler, R.,
        Visual Specifications for Modular Reasoning about Asynchronous Systems,
        In Proceedings of {\em International Conference on Formal Techniques
        for Networked and Distributed Systems (FORTE)}, pp. 226-242, 2002.

\bibitem{amla:03} Amla, N., Kurshan, R.P., McMillan, K.N. and Medel, R., 
         Experimental Analysis of Different Techniques for Bounded Model
         Checking. In {\em International Conference on Tools and 
	 Algorithms for the
         Construction and Analysis of Systems (TACAS)}, pp. 34-48, 2003.

\bibitem{amla4} Amla, N., Emerson, E.A., Namjoshi, K.S. and Trefler, R.,
        Abstract Patterns of Compositional Reasoning,
        In Proceedings of {\em International Conference on Concurrency
        Theory (CONCUR)}, pp. 423-438, 2003.

\bibitem{amla:05} Amla, N.,  Du, X.,  Kuehlmann, A., Kurshan, R.P. and 
	McMillan, K.L. An Analysis of SAT-Based Model Checking Techniques 
	in an Industrial Environment. In {\em International Conference on 
	Correct Hardware Design and Verification Methods (CHARME)}
        pp. 254-268, 2005

\bibitem {ammann:98} Ammann, P.E., Black, P.E., and Majurski, W.,
        Using Model Checking to Generate Test from Specifications, In
        {\em Proc. of 2nd IEEE Int. Conf. on Formal Engineering
        Methods (ICFEM'98)}, IEEE Computer Society, pp. 46-54, 1998.

\bibitem{ahb} {\em ARM AMBA Specification Rev 2.0}, http://www.arm.com

\bibitem{forspec} Armoni, R. {\em et. al.} The ForSpec Temporal Logic:
        A new property-specification language,
        In Proceedings of {\em $8^{th}$ International Conference on Tools and
        Algorithms for the Construction and Analysis of Systems (TACAS)},
        LNCS 2280, pp. 296-311.  Springer Verlag, April 2002. 

%\bibitem{armoni:03} Armoni, R., Fix, L., Flaisher, A., Grumberg, O., 
%	Peterman, N., Tiemeyer, A. and Vardi, M.Y.,
%	Enhanced Vacuity Detection
%        in Linear Time Logic. In {\em Proc. of Computer Aided Verification
%	(CAV)}, LNCS 2725, pp. 368-380, 2003.

\bibitem{ball:01} Ball, T., Majumdar, R., Millstein, T., and 
	Rajamani, S., Automatic predicate abstraction of C programs, 
	In Proc. of ACM SIGPLAN 2001 Conference on Programming Language Design 
	and Implementation (PLDI), pp. 203-213, 2001. 

%\bibitem{vlsi04} Banerjee, A., Dasgupta, P., Chakrabarti, P.P.,
%        Formal Verification of Modules Under Real Time Environment Constraints,
%        In Proceedings of {\em International Conference on VLSI Design (VLSI)},
%        pp. 103-108, 2004.

\bibitem{jason:02} Baumgartner, J., Automatic Structural Abstraction 
	Techniques for Enhanced Verification, Ph.D. dissertation, 
	Dept. of Electrical and Computer Engineering, University of 
	Texas and Austin, 2002. 

\bibitem{bergeron:05} Bergeron, J., Cerny, E., Hunter, A., and
	Nightingale, A., {\em Verification Methodology Manual for System
	Verilog}, Springer Verlag, 2005.

\bibitem{bhadra:07} Bhadra, J., Abadir, M., Wang, L.C., and Ray, S., 
	A Survey of Hybrid Techniques for Functional Verification, 
	In {\em IEEE Design and Test of Computers}, Vol. 24 (2), 
	pp. 112-122, 2007.

\bibitem{biere:99a} Biere, A., Cimatti, A.,  Clarke, E.M., and Zhu, Y.,
	Symbolic Model Checking without BDDs. In {\em Lecture notes in
	Computer Science}, 1579, pp. 193-207, 1999.

\bibitem{biere:99} Biere, A., Cimatti, A., Clarke, E.M., Fujita, M., Zhu, Y.,
        Symbolic Model Checking Using SAT Procedures Instead of BDDs.
        {\em Proc. of Design Automation Conference (DAC)}, 1999, 
	pp. 317-320.

\bibitem{biere:99c} Biere, A., Clarke, E.M., Raimi, R. and Zhu, Y., 
	Verifying Safety Properties of a Power PC Microprocessor Using 
	Symbolic Model Checking without BDDs, In 
	{\em Proc. of Computer Aided Verification
    (CAV)} 1999, pp. 61-71. 

\bibitem{bjesse} Bjesse, P., and Kukula, J.,
        Using counter example guided abstraction refinement to find
        complex bugs, In {\em Proc. of Design Automation and Test in 
	Europe (DATE)}, 2004, pp. 156-161.

\bibitem{blast} BLAST homepage, http://mtc.epfl.ch/software-tools/blast/ 

\bibitem{jobst} Bloem, R. {\em et. al.} Automatic Hardware Synthesis
        from Specifications: A Case Study, 
	In {\em Proc. of Design Automation and Test in 
	Europe (DATE)} 2007, pp. 1188-1193.

\bibitem{boppana:99} Boppana, V., Rajan, S.P., Takayama, K., and Fujita, M.,
        Model Checking Based on Sequential ATPG, In {\em Proc. of Computer 
	Aided Verification (CAV)}, pp. 418-430, 1999.

\bibitem{tocl} Bradfield, J., Kuester, F., and Stevens, P., Enriching
    OCL Using Observational mu-calculus, In {\em Fundamental Approaches 
    to Software Engineering (FASE)}, volume 2306 of LNCS. Springer,
    2002, pp. 203-217.

\bibitem{vis} Brayton, R.K. et al. VIS: A system for verification
        and synthesis, In {\em Proc. of Computer Aided Verification
    (CAV)}, volume 1102 of LNCS, pp. 428-432, 1996.

\bibitem{Bro89} Browne, M.C., Automatic verification of finite state
    machines using temporal logic. PhD thesis, Carnegie Mellon University,
1989. Technical report no. CMU-CS-89-117. 

\bibitem{bryant:86} Bryant, R., Graph-based Algorithms for Boolean-function
	Manipulation. {\em IEEE Trans. on Computers}, Vol. 35 (8), 1986, 
	pp. 677-691.

\bibitem{buchi:69} B$\ddot{u}$chi, J. and Landweber, L., 
	Solving sequential conditions
	by finite state strategies. {\em Trans. of the American Mathematical
	Society}, vol. 138, pp. 295-311, 1969.

\bibitem{burch:90b} Burch, J.R., Clarke, E.M., McMillan, K.L. and Dill, D.L., 
	Sequential Circuit Verification Using Symbolic Model Checking, 
	In {\em Proc. of Design Automation Conference (DAC)} 1991, 
	pp. 46-51.

%\bibitem{burch:91} Burch, J.R., Clarke, E.M., and Long, D.E., Representing
%	circuits more efficiently in symbolic model checking. In {\em
%	Proc. of Design Automation Conference}, 1991.

\bibitem{burch:91a} Burch, J.R., Clarke, E.M., and Long, D.E., Symbolic
	model checking with partitioned transition relations. In {\em
	Proc. of Int. Conf. on VLSI}, 1991, pp. 49-58.

\bibitem{burch:92} Burch, J.R., Clarke, E.M., McMillan, K.L., Dill, D.L.,
	and Hwang, L.J., Symbolic Model Checking: $10^{20}$ states and
	beyond. {\em Information and Computation}, 98(2), pp. 142-170, 1992.

%\bibitem{burch:94} Burch, J.R., Clarke, E.M., Long, D.E., McMillan, K.L.,
%	and Dill, D.L., Symbolic Model Checking for Sequential Circuit
%	Verification. {\em IEEE Trans. on CAD}, 13(4), 401-424, 1994.

\bibitem {callahan:96} Callahan, J., Schneider, F., and Easterbrook, S.,
	Automated Software testing using model-checking, In {\em Proc. of 
	SPIN Workshop}, 1996. 

\bibitem{oclrt} Cengarle, M.V., and Knapp, A., Towards OCL/RT,
    In International Symposium of Formal Methods Europe,
    volume 2391 of LNCS, pp. 389-408, Springer, 2002. 

\bibitem{chaki1} Chaki, S., et al.
    Concurrent software verification with states, events, and deadlocks,
    Formal Aspects of Computing 17(4), 2005, pp. 461-483.

\bibitem{chaki2} Chaki, S., et al.
    State/event software based model checking,
    Fourth International Conference on Integrated Formal Methods
    (IFM) 2004, LNCS 2999, pp. 128-147. 

\bibitem{chandy:81} Chandy, K.M. and Misra, J., Proofs of Networks of Processes,
	In {\em IEEE Transactions on Software Engineering}, Volume SE-7,
	No. 4, pp. 417-426, 1981.

\bibitem{cclw99} Chauhan, P., Clarke, E.M., Lu, Y., and
        Wang, D., Verifying IP-Core based
        System-on-Chip Designs. In Proceedings of ASIC Conference, 1999,
        pp. 27-31.

\bibitem{chauhan:02} Chauhan, P., Clarke, E.M., Kukula, J.H.,
    Sapra, S., Veith, H. and Wang, D., Automated Abstraction Refinement
    for Model Checking Large State Spaces Using SAT Based Conflict
    Analysis, In {\em Proc. of Formal Methods in Computer Aided Design 
    (FMCAD)}, 2002, pp. 33-51.

\bibitem{cho} Cho, H., Hachtel, G.D., Macii, E., Plessier, B.,
        and Somenzi, F., Algorithms for approximate FSM traversal
        based on state space decomposition, In {\em IEEE Transactions
        on Computer-Aided Design of Integrated Circuits}, vol. 15,
        no. 12, pp. 1465-1478, 1996. 

%\bibitem{chockler:01} Chockler, H., Kupferman, O., Kurshan, R.P., and Vardi,
%        M.Y., A practical approach to coverage in model checking, In
%        {\em Proc. of Computer Aided Verification (CAV)}, 66-78, 2001.

%\bibitem{chockler:01a} Chockler, H., Kupferman, O., and Vardi, M.Y.,
%	Coverage metrics for temporal logic model checking. In {\em Proc.
%	of TACAS}, LNCS 2031, 528-542, 2001.

%\bibitem{chockler:02} Chockler, H., and Kupferman, O., Coverage of
%	implementations by simulating specifications. In {\em Proc. of
%	TCS}, 223, 409-421, 2002.

%\bibitem{chockler} Chockler, H., Kupferman, O., and Vardi, M.Y., Coverage
%	Metrics for Formal Verification. In {\em $12^{th}$ Advanced Research
%	Working Conf. on Correct Hardware Design and Verification Methods},
%	LNCS 2860, 111-125, 2003.
%
\bibitem{church:63} Church, A., Logic, Arithmetics and automata, 
		In. Proc. International Congress of Mathematicians, 1962, 
		pp. 23-35.

\bibitem{ce81}  Clarke, E.M. and Emerson, E.A.,  Design and synthesis of
        synchronization skeletons using branching time temporal logic,
        In {\em Logic of Programs: Workshop, Yorktown Heights, NY, May 1981},
        LNCS 131, pp. 52-71, Springer-Verlag, 1981. 

\bibitem{clarke:86}  Clarke, E.M., Emerson, E.A., and Sistla, A.P., Automatic
        verification of finite-state concurrent systems using temporal logic
        specifications, In {\em ACM Transactions on Programming Languages and 
	Systems (TOPLAS)}, 8(2), pp. 244-263, 1986.

\bibitem{clarke:92} Clarke, E.M, Grumberg, O., and Long, D., Model Checking 
	and Abstraction, In Proc. of 19th Annual ACM SIGPLAN-SIGACT Symposium 
	on Principles of Programming Languages, 1992, pp. 343-354.

\bibitem{clarke:94} Clarke, E.M., Grumberg, O., and Hamaguchi, K., Another look
	at LTL model checking, In {\em Proc. of Workshop on Computer Aided
	Verification (CAV)}, 1994, pp. 47-71.

\bibitem{clarke:00} Clarke, E.M., Grumberg, O., and Peled, D.A.,
        {\em Model Checking}, MIT Press, 2000.

\bibitem{clarke:00a} Clarke, E., German, S., Lu, Y., Veith, H., and Wang, D.,
        Executable Protocol Specification in ESL, 
        In {\em Proceedings of Formal Methods in Computer-Aided Design
        (FMCAD)}, 2000, pp. 197-216.

\bibitem{clarke:00b} Clarke, E.M., Grumberg, O., Jha, S., Lu, Y., and
	Veith, H., Counter-example guided abstraction refinement. In
	{\em Proc. of Computer Aided Verification} (CAV), pp. 154-169, 2000.

\bibitem{clarke:01} Clarke, E.M., Biere, A., Raimi, R., and Zhu, Y.,
	Bounded Model Checking using satisfiability solving. {\em Formal
	Methods in System Design}, 19(1), pp. 7-34, 2001.

\bibitem{clarke:02} Clarke, E.M., Gupta, A., Kukula, J.H., and Strichman, O.,
	SAT-based abstraction refinement using ILP and machine learning
	techniques. In {\em Proc. of Computer Aided Verification (CAV)},
	pp. 265-279, 2002.

%\bibitem{courcoubetis:92} Courcoubetis, C., Vardi, M.Y., Wopler, P., and
%	Yannakakis, M., Memory efficient algorithms for the verification
%	of temporal properties. {\em Formal Methods in System Design},
%	1, 275-288, 1992.
\bibitem{bandera} Corbet, J.C., Dwyer, M.B., Hatcli, J., and Robby, 
	Bandera: A source level interface for model checking java 
	programs, In {\em Proc. of 22nd Int. Conf. on Software Engineering}, 
	2000, pp. 762-765.

\bibitem{cro95} Crow, J., Owre, S., Rushby, J., Shankar, N. and Srivas, 
	M., A Tutorial Introduction to PVS, In {\em Proc. of WIFT}, Workshop 
	on Industrial Strength Formal Specification Techniques, 1995, 
	http://www.csl.sri.com/sri-csl-fm.html

%\bibitem{das:04} Das, S., Basu, P., Banerjee, A., Dasgupta, P., Chakrabarti,
%        P.P., Mohan, C.R., Fix, L., Armoni, R., Formal Verification Coverage:
%        Computing the Coverage Gap between Temporal Specifications, In {\em
%        Proc. of ICCAD}, San Jose, 198-203, 2004.

\bibitem{pdgbook} Dasgupta, P., A Roadmap for Formal Property Verification, 
		Springer 2006.

%\bibitem{aspdac02} Dasgupta, P., Chakrabarti, A., Chakrabarti, P.P.,
%        Open Computation Tree Logic for Formal Verification of Modules,
%        In Proceedings of {\em IEEE Asia South Pacific Design Automation
%        Conference (ASPDAC)}, pp. 735-740, 2002. 

%\bibitem{dax:05} Dax, C., and Lange, M., Game Over: The Foci Approach to LTL
%       Satisfiability and Model Checking, Electr. Notes Theor. Comput. Sci.
%        119(1): 33-49, 2005.

\bibitem{dill:89} Dill, D.L., {\em Trace Theory for Automatic Hierarchical
        Verification of Speed-independent Circuits.} ACM Distinguished
        Dissertations. MIT Press, 1989.

\bibitem{emerson:87} Emerson, E.A., and Lei, C.L., Modalities for model
        checking: Branching time strikes back, In
        Proceedings of {\em $12^{th}$ ACM Symposium on Principles of
        Programming Languages}, pp. 84-95, 1985.

\bibitem{emerson:89}  Emerson, E.A., Mok, A.K., Sistla, A.P., and
        Srinivasan, J., Quantitative temporal reasoning, In First Annual
        Workshop on Computer-Aided Verification (CAV), pp. 136-145,
        France, 1990. 

\bibitem{erm} eRM -- e Reuse Methodology,
	http://www.verisity.com/products/erm.html

\bibitem{fisler:02} Fisler, K., and Vardi, M., Bisimulation minimization and
	symbolic model checking. {\em Formal Methods in System Design},
	21(1), pp. 39-78, 2002.

\bibitem{rtocl} Flake, S., and Mueller, W., An OCL Extension for
    Real-Time Constraints. In Object modeling with the OCL:
    The Rationale behind the Object Constraint Language,
    volume 2263 of LNCS, pp. 389-408, Springer, 2002. 

\bibitem{formalpro} FormalPro, 0-In, 
        http://www.mentor.com/products/fv/product\_index.cfm

\bibitem{fut95} Futatsugi, K., Goguen, J., Jounnad, J.P. and 
	Mesguer, J., Principles of OBJ, In {\em Proc. of POPL}, 1985, 
	ACM Symposium on Principles of Programming Languages, pp. 52-66.

%\bibitem{fummi:03} Fummi, F., Pravadelli, G., Fedeli, A., Rossi, U., and
%        Toto, F., On the Use of a High-Level Fault Model to Check
%        Properties Incompleteness, In {\em Proc. of Int. Conf. on Formal 
%	Methods and Models for Codesign (MEMOCODE)}, pp. 145-152, 2003.

\bibitem{ganai:01} Ganai, M., Yalagandula, P., Aziz, A., Kuehlmann, A., 
	and Singhal, V., SIVA: A System for Coverage-Directed State 
	Space Search, Journal of Test Automation: Theory and Applications, 
	2001, pp. 11-27. 

\bibitem {gannon:81} Gannon, J., McMullin, P., and Hamlet, R., 
	Data-Abstraction Implementation, Specification, and Testing, {\em ACM 
	Transactions on Programming Languages and Systems}, 3(3), 
	pp. 211-223, 1981.

\bibitem{gargantini:99} Gargantini, A., and Heitmeyer, C., Using Model 
	Checking to Generate Test from Requirements Specifications; In 
	{\em Proc. of Joint 7th European Software Engineering
        Conf. and 7th ACM SIGSOFT Int. Symp. on Foundations
        of Software Eng. (ESEC/FSE99)}, pp. 146-162, 1999.

%\bibitem{gawlick:94} Gawlick, R., Segala, R., Sogaard-Anderson, J., and
%	Lynch, N.A., Liveness in timed and untimed systems. In {\em Proc.
%	of Int. Coll. on Automata, Languages and Programming}, LNCS Vol 820,
%	166-177, 1994.

\bibitem{GM03} Giannakopoulou, D. and Magee, J., Fluent model checking for
    event-based systems. In Proceedings of the 11th ACM
    SIGSOFT Symposium on Foundations of Software Engineering
    (FSE), pp. 257-266. ACM Press, 2003.

\bibitem{giese} Giese, H. et al,
    Towards the Compositional Verification of Real-Time UML Designs,
    In {\em Proc. of 9th European Software Engineering
    Conf. and 11th ACM SIGSOFT Int. Symp. on Foundations
    of Software Eng. (ESEC/FSE)}, 2003, pp. 38-47.

%\bibitem{qube} Giunchiglia,E., Narizzano, M., Tacchella, A., System
%        Description: QuBE A System for Deciding Quantified Boolean Formulas
%        Satisfiability. In {\em Proc. of Intl. Joint Conf. on Automated
%        Reasoning (IJCAR-01)}, 2001.

\bibitem{godefroid:94} Godefroid, P., and Wolper, P., A partial approach to
	model checking. In {\em Proc. of Logic in Computer Science} (LICS),
	pp. 305-326, 1994.

\bibitem{verisoft} Godefroid, P. Model checking for programming 
	languages using verisoft, In {\em Proc. of 24th ACM Symposium of 
	Principles of Programming Languages (POPL)}, 1997, pp. 174-186.

\bibitem{goldberg} Goldberg, E. and Novikov, Y.  BerkMin: a Fast and Robust
        SAT-Solver, presented at {\em Design Automation \& Test in Europe
        (DATE)}, 2002, pp. 142-149.

\bibitem{gor93} Gordon, M. and Melham, T.F., Introduction to HOL, 
	Cambridge University Press, 1993.

\bibitem{govindaraju:98} Govindaraju, S.G., and Dill, D.L., Verification by
	approximate forward and backward reachability. In {\em Proc. of
	Int. Conf. on Computer Aided Design} (ICCAD), pp. 366-370, 1998.

\bibitem{graf:97} Graf, S. and Saiidi, H., Construction of abstract state 
	graphs in PVS, In Proc. of Int. Conf. on Computer Aided Verification, 
	vo. 1254 of LNCS, pp. 72-83, 1997. 

%\bibitem{grumberg:94} Grumberg, O., and Long, D.E., Model Checking and
%   	Modular Verification, {\em ACM Transactions on Programming Languages
%	and Systems (TOPLAS)}, vol. 16, pp. 843-872, 1994.

\bibitem{gupta:02} Gupta. A.,Casavant. A.E.,Ashar P., and Liu X.G.,
        Property Specific Testbench Generation for Guided Simulation,
        In {\em Proc. of Asia-South-Pacific Design Automation Conference
        (ASP-DAC)}, pp. 524-534, 2002.

\bibitem{gupta:03} Gupta, A., Ganai, M.K., Wang, C., Yang, Z. and Ashar, P.,
	Learning from BDDs in SAT-based bounded model 
	checking. In {\em Proc. of Design Automation Conference (DAC)}
    2003, pp. 824-829.

\bibitem{harding:05} Harding, A., Ryan, M., and Schobbens, P., 
	A new algorithm for strategy synthesis in LTL games, In 
	{\em Proc. of International Conference on Tools and Algorithms for the
        Construction and Analysis of Systems (TACAS)}, 
	LNCS 3440, pp. 477-492, 2005.

\bibitem{rhap} Harel, D. and Kugler, H.,
    The Rhapsody semantics of Statecharts, LNCS vol. 3147, Springer-Verlag,
    pp. 325-354, 2004. 

\bibitem{jpf} Havelund, K., Pressburger, T., Model Checking Java 
	programs using Java Pathfinder, Int. Journal of Software Tools 
	and Technology Transfer, 1999, pp. 366-381. 

\bibitem{mist} Hazelhurst, S., Weissberg, O., Kamhi, G., and Fix, L., 
	A hybrid verification approach: Getting deep into the design, 
	In {\em Proc. of Design Automation Conference (DAC)} 2002, 
	pp. 111-116.

\bibitem{henzinger:00} Henzinger, T., Qadeer, S., and Rajamani, S.,
        Decomposing Refinement Proofs using Assume-Guarantee Reasoning,
        In Proceedings of {\em International Conference on Computer-Aided 
	Design (ICCAD)}, pp. 245-252, 2000.

\bibitem{ho} Ho, P.-H. et al., Smart Simulation using Collaborative
        Formal and Simulation Engines, In {\em Proc. of International 
	Conference on Computer-Aided Design (ICCAD)} 2000, pp. 120-126.

\bibitem{Hoa85} Hoare, C.A.R., An Axiomatic Basis for Computer 
	Programming, In {\em Comm. ACM}, Vol. 12 No. 12 No. 10, 1969, 
	pp. 576-583.

\bibitem{holzmann:94} Holzmann, G.J., and Peled, D., An improvement 
	in formal verification, In {\em Proc. of 7th Int. Conf. on Formal 
	Description Techniques (FORTE)} 1994, pp. 197-211.

\bibitem{feaver} Holzmann, G.J., and Smith, M., Software Model Checking: 
	In {\em Proc. 
	of 7th Int. Conf. on Formal Description Techniques (FORTE)}
	1999, pp. 481-497.

%\bibitem{hoskote:99} Hoskote, Y., Kam, T., Ho, P.H., and Zao, X., Coverage
%        estimation for symbolic model checking, In {\em Proc. of Design 
%	Automation Conference}, 1999.

\bibitem{huang:02} Huang, C.Y., and Cheng, K.T., Assertion Checking by
	combined word-level ATPG and modular arithmetic constraint-solving
	techniques, In {\em Proc. of Design Automation Conference}, 
	pp. 118-123, 2002.

%\bibitem{hughes:77} Hughes, G.E., and Creswell, M.J., {\em Introduction to
%	Modal Logic}, Methuen, 1977.

\bibitem{HJS01} Huth, R. and Schmidt. Modal transition
    systems: A foundation for three-valued program analysis. In Proceedings
   of the 10th European Symposium on Programming (ESOP), volume 2028 of
    Lecture Notes in computer Science, pp. 137-154. Springer, 2001. 

\bibitem{ibmcc} IBM CoreConnect, 
	http://www-306.ibm.com/chips/techlib/techlib.nsf/techdocs

\bibitem{ifv} Incisive, 
        http://www.cadence.com/products/functional\_ver/index.aspx

\bibitem{jones} Jones, C.B., Specification and Design of Parallel Programs,
        In Proceedings of {\em International Conference of International
        Federation for Information Processing (IFIP)}, pp. 321-332,
        1983.

\bibitem{josko} Josko, B., Verifying the correctness of AADL Modules using
        model checking, LNCS, vol. 430, pp. 386-400, Springer Verlag, 1999.

\bibitem{kang:03} Kang, H.J., and Park, I.C., SAT-based unbounded model
	checking. In {\em Proc. of Design Automation Conference}, pp. 840-843,
	2003.

\bibitem{kmp98} Kaufman, M., Martin, A., and Pixley, C.,
        Design Constraints in Symbolic Model Checking,
        In {\em Proc. of International Conference on Computer-Aided 
	    Verification (CAV)}, pp. 477-187, 1998. 

\bibitem{KV98} Kindler, E. and Vesper, T., ESTL: A temporal logic for events
    and states. In Proceedings of the 19th International Conference on the
    Application and Theory of Petri Nets (ICATPN), volume 1420 of Lecture
    Notes in Computer Science, pp. 365-383. Springer, 1998. 

\bibitem{kuehl} Kuehlmann, A., McMillan, K., and Brayton, R.,
        Probabilistic state space search, 
	In {\em Proc. of Int. Conf. on Computer
	Aided Design} (ICCAD) 1999, pp. 574-580.

\bibitem{kupferman:96} Kupferman, O. and Vardi, M.Y., Module Checking, In
        Proceedings of {\em $8^{th}$ International Conference on 
	Computer Aided Verification (CAV)}, LNCS 1102, pp. 75-86, 1996.

%\bibitem{vardi:95} Kupferman, O., and Vardi. M., Weak Alternating Automata
%	are not that weak. In {\em 5th Israel Symp. on the Theory of Computing
%	Systems}, 1997.

%\bibitem{kupferman:99} Kupferman, O. and Vardi, M.Y., Vacuity Detection
%        in Temporal Model Checking, In Proceedings of 
%	{\em $10^{th}$ International Conference on Correct
%	Hardware Design and Verification Methods (CHARME)}, 
%	LNCS 170, pp. 82-96, Springer-Verlag, 1999.

%\bibitem{kupferman:03} Kupferman, O. and Vardi, M.Y., Vacuity Detection
%        in Temporal Model Checking, {\em Int. Journal of Software Tools
%        for Technology Transfer (STTT)}, 4(2) pp. 224-233, 2003.

\bibitem{kupferman:05} Kupferman, O. and Vardi, M.Y., Safraless Decision 
		Procedures, In Proceedings of $46^{th}$ IEEE Symposium on 
		Foundations of Computer Science, pp. 531-540, 2005.

\bibitem{kurshan:94} Kurshan, R.P., Computer Aided Verification 
	of Coordinating Processes: The Automata Theoretic approach,
	Princeton University Press, 1994.

%\bibitem{lamport:80} Lamport, L., "Sometimes" is sometimes "Not Never".
%	In {\em Proc. of ACM Symp. on Principles of Prog. Lang.}, 174-185,
%	1980.

\bibitem{ltlp} Laroussinie, F., Markey, N. and Schnoebelen, P., 
	Temporal logic with forgettable past. In {\em Proc. 17th IEEE
	Symp. Logic in Computer Science (LICS)},
	pp. 383-392, 2002.

\bibitem{li:03} Li, B., Wang, C. and Somenzi, F., A 
	satisfiability-based approach to abstraction refinement in 
	model checking. {\em Electr. Notes Theor. Comput. Sci.  
	Volume 89-4 2003.} 

\bibitem{lichtenstein:85} Lichtenstein, O., and Pnueli, A., Checking that
	finite state concurrent programs satisfy their linear specification.
	In {\em Proc. of ACM Symp. on Principles of Programming Languages},
	pp. 97-107, 1985.

\bibitem{lin} Local Interconnect Protocol, 
	http://www.lin-subbus.org/ 

\bibitem{loding} L\"oding, C., Optimal bounds for the transformation of 
		omega-automaton, In. Proc. of 19th Conference on Foundations of 
		Software Technology and Theoretical Computer Science, Vol. 
		1738 of LNCS, 1999, pp. 97-109.

\bibitem{LTSA} LTSA website.
    http://www-dse.doc.ic.ac.uk/concurrency/ltsa/LTSA.html 

\bibitem{magellan} Magellan - Hybrid RTL Formal Verification, \\
        http://www.synopsys.com/products/magellan/

\bibitem{mw84} Manna, Z., and Wolper, P., Synthesis of communicating
    processes from temporal logic specifications, ACM Trans. Prog.
    Lang., Vol. 6, pp. 68-93, 1984. 

\bibitem{mcmillan:93} McMillan, K.L., {\em Symbolic Model Checking},
	Kluwer Academic Publishers, 1993.

\bibitem{mcmillan:02} McMillan, K.L., Applying SAT Methods in Unbounded 
	Symbolic Model Checking. In {\em Proc. of the 14th Intl. Conf on 
	Computer Aided Verification (CAV)}, Springer Verlag 2002, 
	pp. 250-264.

\bibitem{mcmillan} Mcmillan, K.L.,
        Circular Compositional Reasoning about liveness,
        In Proceedings of {\em International Conference on Correct
        Hardware Design and Verification Methods (CHARME)},
        vol. 1703 of LNCS, pp. 342-345, 1999. 

%\bibitem{misra} Mishra, B., Clarke, E.M.,
%        Hierarchical Verification of asynchronous circuits using
%        temporal logic, In {\em Theoretical Computer Science}, vol. 38,
%        pp. 269-291, 1985. 

\bibitem{mhg98} Mokkedem, A., Hosabettu, R., and Gopalakrishnan, G.,
        Formalization and Proof of a Solution
        to the PCI 2.1 Bus Transaction Reordering Problem,
        In FMCAD, pp. 237-254, 1998.

\bibitem{sixth:85} Mony, H., Baumgartner, J., Paruthi, V., Kanzelman, 
	R., and Kuehlmann, A., Scalable Automatic Verification via 
	Expert-System Guided Transformations, In {\em Formal Methods in 
	Computer-Aided Design (FMCAD)}, 2004, pp. 159-173.

\bibitem{moore} Moore, G.E. Cramming more components onto integrated
	circuits, 1965 Electronics 38, pp. 114-117, 1965.

\bibitem{zchaff} Moskewicz, M., Madigan, C.F., Zhao, Y., Zhang, L. and 
	Malik, S.,
        Chaff: Engineering an Efficient SAT Solver. {\em Proc. of Design
	Automation Conference}, 2001,  pp. 530-535.

\bibitem{muller} Muller, D.E. and Schupp, P.E., Simulating Alternating Tree 
	Automata by Nondeterministic Automata, New Results and New Proofs of 
	the Theorems of Rabin, McNaughton and Safra, Theoretical Computer 
	Science 141 (1\&2) 1995, pp. 69-107.

\bibitem{myers:79} Myers, G.J., Art of Software Testing, John Wiley and 
	Sons, Inc. 1979

\bibitem{namjoshi} Namjoshi, K. and Trefler, R.J.,
        On the completeness of Compositional Reasoning,
        In Proceedings of {\em International Conference on Computer
        Aided Verification (CAV)}, vol. 1855 of LNCS, pp. 139-153, 2000. 

\bibitem{kunz} Nguyen, D. M., Stoffel, D., Wedler, M., and
        Kunz, W., Transition-by-Transition FSM Traversal
        for Reachability analysis in Bounded Model Checking,
        In {\em Proc. of Int. Conf. on Computer
	Aided Design} (ICCAD) 2005, pp. 1060-1067.

\bibitem{NV95} Nicola, R.D. and Vaandrager, F. Three logics for branching
    bisimulation. Journal of the ACM, Vol. 42(2), pp. 458-487, 1995. 

\bibitem{NFGR93} Nicola, R.D., Fantechi, A., Gnesi, S. and Ristori, G., An
    action-based framework for verifying logical and behavioral properties
    of concurrent systems. Computer Networks and ISDN Systems,
    Vol. 25(7), pp. 761-778, 1993. 

\bibitem{nusmv} NuSMV: a new symbolic model checker, http://nusmv.irst.itc.it/

\bibitem{uml} Object Management Group, {\em Unified Modelling
	Language Specification}, Version 1.4, Draft, OMG(2001),
	http://cgi.omg.org/cgibin/docad/018214. 

\bibitem{open} OpenCores, http://www.opencores.org/

\bibitem{ova} OpenVera Assertions LRM 2.0. http://www.open-vera.com

\bibitem{ovl} Open Verification Library, 
	http://www.accellera.org/activities/ovl.

\bibitem{panda} Pandya, P. and Joseph, M., P-A logic - a compositional
        proof system for distributed programs,
        In {\em Distributed Computing}, vol. 5, pp. 37-54, 1991. 

\bibitem{pci} PCI Local Bus Specification Revision 2.2 (1998), \\
        http://www.pcisig.com/specifications/conventional

\bibitem{peled:93} Peled, D., All from one, one for all: on model checking
	using representatives. In {\em Proc. of Computer Aided Verification}
	(CAV), pp. 409-423, 1993.

\bibitem{peled:94} Peled, D., Combining partial order reductions with 
	on-the-fly model checking, In {\em Proc. of 6th Int. Conf. on 
	Computer Aided Verification (CAV)}, 1994, pp. 377-390.

\bibitem{perry:05} Perry, D., and Foster, H., {\em Applied Formal 
	Verification}, McGraw Hill, 2005.

\bibitem{nir} Peterman, N., Pnueli, A., and Sa'ar, Y.,
    Synthesis of Reactive(1) Designs, In Conference on
    Verification, Model Checking and Abstract Interpretation,
    pp. 364-380, 2006. 

\bibitem{pnueli:77} Pnueli, A., The Temporal Logic of Programs. In
        {\em Proc. of Foundations of Computer Science}, pp. 46-57, 1977.

\bibitem{pnueli:84} Pnueli, A., In transition from global to modular temporal
	reasoning about programs. In {\em Logics and Models of Concurrent
	Systems}, Vol 13 of NATO ASI series, Springer Verlag, 1984, pp. 123-144.

\bibitem{pnueli:89} Pnueli, A. and Rosner, R., On the Synthesis of a Reactive
	Module. In {\em Proc. of the 16th ACM Symposium on the Principles of
        Prog. Lang.}, 1989, pp. 179-190.

\bibitem{psl} Property Specification Language, http://www.eda.org/ieee-1850 

\bibitem{prosyd} PROSYD project, http://www.prosyd.org 

\bibitem{rab:72} Rabin, M. O., Automata on Infinite Objects and Church's 
	problem, Vol. 13 of Regional Conference Series in Mathematics, 
	Amer. math Society, 1972.

\bibitem{rvm} Reference Verification Methodology (RVM) for Vera, \\
        http://www.synopsys.com/products/simulation/pdf/va\_vol4\_iss1\_vera.pdf

\bibitem{rhapsody} Rhapsody homepage,
    http://modeling.telelogix.com

\bibitem{roever} Roever, W-P., The need for Compositional Proof Systems:
        A Survey,
        In {\em International Symposium on Compositionality: The Significant
        Difference (COMPOS)}, vol. 1536 of LNCS, pp. 1-22, 1997. 

\bibitem {safra:88} Safra, S., On the Complexity of $\omega$ automata, 
	In Proc. of 29th Foundations of Computer Science, 1988, pp. 319-327.

\bibitem{schloer} Schl$\ddot{o}$r, R.C., Symbolic Timing Diagrams: A Visual
        formalism for Model Verification, Ph.D. Thesis,
        University of Oldenburg, 2000. 

\bibitem{schnoebelen:02} Schnoebelen, P., The complexity of temporal logic
	model checking. In Advances in Modal Logic, papers from {\em 4th 
	Int. Workshop on Advances in Modal Logic (AiML'2002)}, 
	2002, pp. 393-436.

\bibitem{gste1} Sebastiani, R. et al., GSTE is partitioned model
        checking, In {\em Proc. of Computer Aided Verification (CAV)} 
	2004, pp. 229-241.

\bibitem{room} Selic, B., Gullekson, G., and Ward, P., Real-Time
    Object-Oriented Modeling. John Wiley \& Sons, Inc., 1994. 

\bibitem{umlrt} Selic, B., Rumbaugh, J.,
    Using UML for modeling complex real-time systems.
    Techreport, ObjectTime Limited, 1998. 

\bibitem{gd00} Shankar S.G., and Dill, D., Counterexample-guided
        choice of projections in approximate symbolic model
        checking, In {\em Proc. of Int. Conf. on Computer
	Aided Design} (ICCAD) 2000, pp. 115-119.

\bibitem{sheng:02} Sheng, S., Takayama, K., and Hsiao, M.S., Effective safety
	property checking using simulation-based sequential ATPG. In {\em
	Proc. of Design Automation Conference (DAC)}, pp. 813-818, 2002.

\bibitem{dill:00} Shimizu K., Dill, D., and Hu, A.J.,
        Monitor-Based Formal Specification of PCI, In {\em Formal Methods 
	in Computer-Aided Design (FMCAD)} 2000, pp. 335-353.

\bibitem{dill:01} Shimizu K., Dill, D., and Chou, C.,
        A Specification Methodology by a
        Collection of Compact Properties as Applied to the Intel
        Itanium Processor Bus Protocol, In 
	Proceedings of {\em International Conference on Correct
        Hardware Design and Verification Methods (CHARME)} 2001, pp. 340-354. 

\bibitem {shimizu:02} Shimizu, K., and Dill, D.L., Deriving a simulation input
        generator and a coverage metric from a formal specification, In
        {\em Proc. of Design Automation Conference (DAC)}, 
        New Orleans, pp. 801-806, 2002.

\bibitem{guido} Shyam, S., and Bertacco, V., Distance-Guided
        Hybrid Verification with GUIDO, In {\em Design Automation and 
	Test in Europe (DATE)} 2006, pp. 1211-1216.

\bibitem{silva:99} Silva, M. and Sakallah, K.A. GRASP: A Search 	
	Algorithm for Propositional Satisfiability. {IEEE Transaction on 
	Computing, Volume 48(5), pp. 506-521, 1999.} 

%\bibitem{sistla:87} Sistla, A.P., and Clarke, E.M., The complexity of
%	propositional linear temporal logics. {\em Journal of the ACM},
%	32(3), 733-749, 1985.

\bibitem{slam} SLAM Website, http://research.microsoft.com/slam

\bibitem{somenzi:98} Somenzi, F., {\em CUDD: CU Decision Diagram Package,
	    Release 2.3.0, User's Manual}, Dept. of Electrical and Computer
   	    Engineering, University of Colorado, Boulder, 1998.

\bibitem{spin} Spin - Formal Verification, http://www.spinroot.com

\bibitem{stark} Stark, E., A Proof technique for Rely/Guarantee
        Properties, In Proceedings of {\em International Conference on
        Foundations of Software Technology and Theoretical Computer
        Science (FST\&TCS)}, pp. 369-391, 1985. 

\bibitem {stocks:96} Stocks, P. and Carrington, D., A Framework for
    	specification-based testing, {\em IEEE Transactions on Software 
	Engineering}, 22(11), pp. 777-793, 1996.

%\bibitem{sugar} Sugar Formal Property Language Reference Manual.\\
%         http://www.haifa.il.ibm.com/projects/verification/sugar/

\bibitem{sva} System Verilog. http://www.systemverilog.org/

\bibitem{tasiran:03} Tasiran, S., Yuan, Y. and Batson, B., Using a formal
        specification and a model checker to monitor and direct
        simulation, In {\em Proc. of Design Automation Conference (DAC)}, 
        pp. 356-361, 2003.

\bibitem{texas} {\em Texas-97 Verification Benchmarks}, \\
    http://www-cad.eecs.berkeley.edu/Respep/Research/vis/texas-97/

\bibitem{dltl} Thiagarajan, J. and Henriksen, P.S.,
        Dynamic Linear time Temporal Logic,
        In {\em Annals of Pure and Applied Logic}, Volume 96, No. 1-3,
        pp. 187-207, 1999. 

\bibitem{vardi:86} Vardi, M.Y., and Wolper, P., An automata-theoretic approach
	to automatic program verification. In {\em Proc. of Logic in Computer
	Science} (LICS), 1986, pp. 332-344.

%\bibitem{Vardi:97} Vardi, M., Verification of Open Systems,
%         In {\em Proc. of Int. Conf. on
%         Foundations of Software Technology and Theoretical Computer
%         Science (FST\&TCS)}, pp. 250-266, 1997.

\bibitem{vcs} VCS,
        http://www.synopsys.com/products/simulation/ 

\bibitem{wang:03} Wang, C., Li, B., Jin, H., Hachtel, G.D., and Somenzi, F.,
	Improving ariadneys bundle by following multiple threads in
	abstraction refinement. In {\em Proc. of Int. Conf. on Computer
	Aided Design} (ICCAD), pp. 408-415, 2003.

\bibitem{ho1} Wang, D., Ho, P.H., Long, J., Kukula, J., 
	Zhu, Y., Ma, T. and Damiano, R., Formal Property Verification by
        Abstraction Refinement with Formal, Simulation and Hybrid
        Engines, In {\em Proc. of Design Automation Conference (DAC)}, 
	2001, pp. 35-40.

\bibitem{yang} Yang, C.H., and Dill, D., Validation with guided
        search of the state space. In {\em Proc. of Design Automation 
	Conference (DAC)} 1998, pp. 599-604. 

\bibitem{yuan} Yuan, J., Shen, J., Abraham, J., and Aziz, A.,
        On Combining Formal and Informal Verification, In
        {\em Proc. of Computer-Aided Verification (CAV)} 1997, pp. 376-387.

\bibitem{zav82} Zave, P., An Operational Approach to Requirements 
	Specification for Embedded Systems, In {\em IEEE Transactions on 
	Software Engineering}, Vol. 8 No. 3, May 1982, pp. 250-269

\bibitem{quaffle} Zhang, L., and Malik, S., Conflict Driven Learning in a
        Quantified Boolean Satisfiability Solver. In {\em Proc. of the Intl.
        Conf. on Computer-Aided Design (ICCAD)}, 2002, pp. 442-449.

\end{thebibliography}
}
